### 2022-09-21 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@21e2776218f9a4e3445b3f5611cc8342bffe0545 🚀

\begin{itemize}
\tightlist
\item
  It means the probability that two taxa will interact, regardless of
  biological plasticity and environmental variability.
\item
  What do we mean by two taxa will interact? That at least one
  individual from one group will interact with (e.g., predate) at least
  one other individual from the other group.
\item
  The probability is conditional on the environmental and local
  abundance contexts.
\item
  We should expect a certain number of interactions to occur depending
  on the probability value. This number depends on the number of trials,
  which is defined according to the ecological context (e.g.,
  environmental conditions, scale) in which probabilities were
  estimated. This is in contrast with probabilities in metawebs.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Difference of interpretation between probabilities in networks at the
  individual level and at any higher taxonomic level.
\item
  How does the scaling up of the nodes from an individual to population
  to taxonomic group group change our interpretation of interaction
  probabilities? How does the aggregation change the interpretation?
\item
  How is it analogous to spatial and temporal scaling? Basically, all
  kinds of scaling are just different ways to aggregate individuals or
  nodes.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Non-ecological Networks: What can we learn from other systems/fields
  (e.g., social networks, probabilistic graph theory)?
\item
  What even are the probabilities? What is the probability that we will
  ever know the answer to that?
\item
  Be careful how we define probabilities. Be sure to be explicit about
  these things. Be sure to specify the type of interaction, the spatial,
  temporal, and taxonomic scale when presenting new data on interaction
  probabilities. We need better metadata documentation.
\item
  Be careful to use and manipulate interaction probabilities properly
  depending on how they were defined. Different interpretations imply
  different scaling, and thus different ways to manipulate these
  numbers.
\item
  Maybe mention thinking about a workflow to predict probabilistic local
  networks from probabilistic metawebs.
\end{itemize}

>>>>

\begin{itemize}
\tightlist
\item
  It means the probability that two taxa will interact at a given
  location.
\item
  What do we mean by two taxa will interact? That at least one
  individual from one group will interact with (e.g., predate) at least
  one other individual from the other group.
\item
  The probability is conditional on the environmental and local
  abundance contexts.
\item
  We should expect a certain number of interactions to occur depending
  on the probability value. This number depends on the number of trials,
  which is defined according to the ecological context (e.g.,
  environmental conditions, scale) in which probabilities were
  estimated. This is in contrast with probabilities in metawebs.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Difference of interpretation between probabilities in networks at the
  individual level and at any higher taxonomic level.
\item
  How does the scaling up of the nodes from an individual to population
  to taxonomic group change our interpretation of interaction
  probabilities? How does the aggregation change the interpretation?
\item
  How is it analogous to spatial and temporal scaling? Basically, all
  kinds of scaling are just different ways to aggregate individuals or
  nodes.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Non-ecological networks: What can we learn from other systems/fields
  (e.g., social networks, probabilistic graph theory)?
\item
  What even are probabilities? What is the probability that we will ever
  know the answer to that?
\item
  Be careful how we define probabilities. Be sure to be explicit about
  these things. Be sure to specify the type of interaction, the spatial,
  temporal, and taxonomic scale when presenting new data on interaction
  probabilities. We need better metadata documentation.
\item
  Be careful to use and manipulate interaction probabilities properly
  depending on how they were defined. Different interpretations imply
  different scaling, and thus different ways to manipulate these
  numbers.
\item
  Maybe mention thinking about a workflow to predict probabilistic local
  networks from probabilistic metawebs.
\end{itemize}
